Title Goes Here

### 2020-04-21 analysis/paper/paper.Rmd
not working...

#a scatterplot matrix of Correlation
pairs(DF)

# Plot for SCOR
library(corrplot)
corrplot(SCOR, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

corrplot(COR$r, type="upper", order="hclust", 
         p.mat = COR$P, sig.level = 0.01, insig = "blank")
```

>>>>

#a scatterplot matrix of Correlation
ALL<-pairs(DF)

# correlation per phase
cor2 <- 
df_sitename %>% 
  filter(SPstage.Stage == 2) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  cor(.)

ACOR2 <- pairs(cor2)

cor3 <- 
df_sitename %>% 
  filter(SPstage.Stage == 3) %>% 
  select(-sitename, -SPstage.Stage) %>% 
  cor(.)

ACOR3 <- pairs(cor3)

# Plot for SCOR
library(corrplot)

corrplot(COR$r, type="upper", order="hclust", 
         p.mat = COR$P, sig.level = 0.01, insig = "blank")

# correlation for all
cplotall <- corrplot(SCOR, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
# for phase 2
cplot2 <- corrplot(cor2, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
# for phase 3
cplot3 <- corrplot(cor3, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

library(patchwork)

library(gridExtra)
